%% get rid of autoindent   :setl noai nocin nosi inde=
\documentclass{letter} 

\newcommand{\bmu}{\mbox{\boldmath $u$\unboldmath}}

\date{\today}


\begin{document}
\begin{letter}{
Communications on Applied Mathematics and Computation  \\
Dr. Chi-Wang Shu, Editor-in-Chief\\}
	
\opening{Dear Dr. Chi-Wang Shu}
Please find enclosed the revised version of our 
manuscript (CAMC-D-22-00243):
``An improved coupled level set and continuous 
moment-of-fluid method for simulating multiphase flows 
with phase change.''
We thank the reviewer for his/her comments and thoughts 
regarding improvement of our paper. 
In addition to the modifications in response to the reviewers'
suggestions, some improvements have been made to our paper.
\begin{enumerate}
\item The ``method overview'' (section 4.1 now) gives more details: e.g. about
$\Delta t$ and when the level set function is ``redistanced'' (every time step
after advection).  
\item Algorithmic details that can be found in our previous work has been 
  deleted (appropriate citations are kept): CISL advection, viscous solver,
  and projection solver (on AMR hierarchical grid).  We have kept the 
  discretization details of how the exact signed distance to the multi-material
  CMOF reconstructed interface is found (as this is a coupling step) 
  (section 4.3).
\item The added mass algorithm has been improved.  Section 5.4.1, ``Added
  Mass model for static freezing problem'' has been modified accordingly.
  All of the effected freezing results were recomputed (the results changed
  very little).
\end{enumerate}	
We believe that we have addressed all of the reviewers'
concerns; the changes are itemized in detail below.\par 
\par\noindent
NOTE: all references to equations and figures below are with
reference to the numbering scheme of the revised version of the paper,
not the original version.  
%%Also, we have hi-lighted the major
%%changes to our article in 
%%\textcolor{red}{red}.  Also, if most of a section was modified, we
%%hi-lighted just the section heading in \textcolor{red}{red}.
\par\noindent
Changes made in response to comments of the Reviewer: \par 
\begin{enumerate}
\item 
\begin{verbatim}
1- The introduction goes straight to the heart of the 
problem and therefore immediately leads the 
reader to the "action". I have personnaly 
enjoyed it, but I suggest that the authors provide 
some context about free boundary problem; otherwise, 
readers less current on the literature may be disoriented. 
\end{verbatim}
\par 
\vspace{0.5cm}
Response: \\
We have added a new section ``Background - deforming boundary problems in fluid mechanics'' which addresses the reviewers' comments.
\vspace{0.5cm}
\item 
\begin{verbatim}
2- The mathematical description of the different domains and 
interfaces use the level-set formalism but no introduction 
is given on the level-set representation. I also suspect 
that the level-set used is the signed distance function 
(at least reinitialized every x iterations)?
\end{verbatim}
\par 
\vspace{0.5cm}
Response: \\
We have added a new Figure to the paper (added to the new section) which
illustrates the level set distance function property.  Also we have
added in two different places exactly when the level set function is 
reinitialized.
\vspace{0.5cm}
\item 
\begin{verbatim}
3- Some of the section titles are not formatted correctly.
\end{verbatim}
\par 
\vspace{0.5cm}
Response: \\
We double checked all of the section titles and found that they were ok?
Please advise.
\end{enumerate}

\closing{On behalf of the authors, \\ Mark Sussman}

\end{letter}


\bibliography{references}
\bibliographystyle{plain}
\end{document}

